Analysis

### 2017-03-26 Analysis.Rmd
Add notes about analysis to Analysis.Rmd

@@

## Tiller Sheath Blight Severity Model
```{r}

>>>>

Before the analysis, note that due to changes between the years, the analysis
must be carried out on each year separately. The 2015 data and 2016 data cannot
be combined due to changes in inoculation methods; there are other changes too,
but the main one is this. Therefore, the analyses will be conducted separately for
leaf severity and tiller severity for 2015 dry season and 2016 dry season.
Comparisons will only be observational and cannot be statistically compared.

@@

## 2016 Tiller Sheath Blight Severity Model
```{r}
